### 2013-07-30 appa.tex
QQ papersubmit

\begin{table}[ht]
	\[
	\begin{array}{rll}
		\text{Map} & \text{Modules} & \text{Description} \\[1em]
		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
		\barbell{half_bot} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
		\barbell{tri_up} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
		\barbell{id} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
	\end{array}
	\]
	\caption{Describing the maps.}
	\label{tab:prim_maps}
\end{table}

@@

Henceforth, we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.  It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.  With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.

@@

\setcounter{op}{-1}
\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
\begin{remark*}
	The justification for the above operation is not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
\end{remark*}
\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$.  \end{op}
\begin{op}[The Needle] We have $\barbell{needle} = 0$.  \end{op}
\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well. In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.  \end{remark*}
\begin{op}[Barbell-Forcing Rules]
	We have the following three equalities:
	\begin{enumerate}[(a)]
		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_red}$.
		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_blue}$.
	\end{enumerate}
\end{op}

>>>>

\begin{table}[ht]
	\[
	\begin{array}{rll}
		\text{Map} & \text{Modules} & \text{Description} \\[1em]
		\barbell{\includegraphics{barbell/half_top.pdf}} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
		\barbell{\includegraphics{barbell/half_bot.pdf}} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
		\barbell{\includegraphics{barbell/tri_down.pdf}} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
		\barbell{\includegraphics{barbell/tri_up.pdf}} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
		\barbell{\includegraphics{barbell/id.pdf}} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
	\end{array}
	\]
	\caption{Describing the maps.}
	\label{tab:prim_maps}
\end{table}

@@

Henceforth, we will make the convenient abbreviation of $\barbell{\includegraphics{barbell/tri_up_contract_before.pdf}}$ as $\barbell{\includegraphics{barbell/tri_up_contract_after.pdf}}$.  It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.  With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.

@@

\setcounter{op}{-1}
\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
\begin{remark*}
	The justification for the above operation is not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
\end{remark*}
\begin{op}[Associativity] We have $\barbell{\includegraphics{barbell/assoc_horiz.pdf}} = \barbell{\includegraphics{barbell/assoc_vert.pdf}}$.  \end{op}
\begin{op}[Contraction] We have $\barbell{\includegraphics{barbell/contract_left.pdf}} = \barbell{\includegraphics{barbell/contract_right.pdf}} = \barbell{\includegraphics{barbell/alpha_blue.pdf}}$.  \end{op}
\begin{op}[The Needle] We have $\barbell{\includegraphics{barbell/needle.pdf}} = 0$.  \end{op}
\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{\includegraphics{barbell/zero.pdf}}$ is zero as well. In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.  \end{remark*}
\begin{op}[Barbell-Forcing Rules]
	We have the following three equalities:
	\begin{enumerate}[(a)]
		\ii $\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} + \barbell{\includegraphics{barbell/alpha_blue.pdf}} \barbell{\includegraphics{barbell/barbell_blue.pdf}} = 2 \barbell{\includegraphics{barbell/break_blue.pdf}}$, and the similar equation for red.
		\ii $\barbell{\includegraphics{barbell/alpha_red.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}} = -x\barbell{\includegraphics{barbell/break_red.pdf}} + \barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_red.pdf}} + x \barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_red.pdf}}$.
		\ii $\barbell{\includegraphics{barbell/alpha_blue.pdf}}\barbell{\includegraphics{barbell/barbell_red.pdf}} = -y\barbell{\includegraphics{barbell/break_blue.pdf}} + \barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} + y \barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}}$.
	\end{enumerate}
\end{op}

### 2013-07-30 paper.tex
QQ papersubmit

\begin{definition}
	A connected component which
	\begin{inparaenum}[(i)]
		\ii is acyclic, and 
		\ii does not touch the top or bottom boundaries
	\end{inparaenum} is called a \emph{barbell}.
\end{definition}
Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{barbell_blue}$.  Similarly, every red barbell is simply $\barbell{barbell_red}$.

@@

In order to study these maps as algebraic structures, we wish to consider full-maps as polynomials in $\RR[x,y][\alpha_s,\alpha_t]$.  Hence, we establish the following conventions:
\begin{enumerate}
	\ii For any $f \in R$, the map $x \mapsto fx$ (i.e. multiplication on the left) will be abbreviated as $f$ from this point forward.  
	\par In particular, the map $\barbell{barbell_blue}$ is $\alpha_s$.  This follows from a straightforward computation.  Furthermore, one can check that, for example, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.  
	Note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
	\ii We work \emph{modulo lower terms}.  That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.  So, for example, we have $\barbell{break_blue} = 0$.
\end{enumerate}
Henceforth, we refer to diagrams and their associated polynomials interchangeably.

@@

In fact, we can even show that, with this new convention, that the following identity holds for every $f$:
\begin{equation}
	\barbell{alpha_blue} f = \partial_s(f) \barbell{break_blue} + s(f) \barbell{alpha_blue}
	\label{eq:barbell_break}
\end{equation}
where $\partial_s$ is the Demazure operator defined in Appendix~\ref{sec:prelim_genrel}.

>>>>

\begin{definition}
	A connected component which
	\begin{inparaenum}[(i)]
		\ii is acyclic, and 
		\ii does not touch the top or bottom boundaries
	\end{inparaenum} is called a \emph{barbell}.
\end{definition}
Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{\includegraphics{barbell/barbell_blue.pdf}}$.  Similarly, every red barbell is simply $\barbell{\includegraphics{barbell/barbell_red.pdf}}$.

@@

In order to study these maps as algebraic structures, we wish to consider full-maps as polynomials in $\RR[x,y][\alpha_s,\alpha_t]$.  Hence, we establish the following conventions:
\begin{enumerate}
	\ii For any $f \in R$, the map $x \mapsto fx$ (i.e. multiplication on the left) will be abbreviated as $f$ from this point forward.  
	\par In particular, the map $\barbell{\includegraphics{barbell/barbell_blue.pdf}}$ is $\alpha_s$.  This follows from a straightforward computation.  Furthermore, one can check that, for example, $\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} = \alpha_s^2 \alpha_t$.  
	Note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{\includegraphics{barbell/alpha_blue.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}} \neq \alpha_s$.
	\ii We work \emph{modulo lower terms}.  That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.  So, for example, we have $\barbell{\includegraphics{barbell/break_blue.pdf}} = 0$.
\end{enumerate}
Henceforth, we refer to diagrams and their associated polynomials interchangeably.

@@

In fact, we can even show that, with this new convention, that the following identity holds for every $f$:
\begin{equation}
	\barbell{\includegraphics{barbell/alpha_blue.pdf}} f = \partial_s(f) \barbell{\includegraphics{barbell/break_blue.pdf}} + s(f) \barbell{\includegraphics{barbell/alpha_blue.pdf}}
	\label{eq:barbell_break}
\end{equation}
where $\partial_s$ is the Demazure operator defined in Appendix~\ref{sec:prelim_genrel}.
